\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-24 icse20/compiler.tex
Slight updates in evaluation
assitant -> fault localizer

\subsection{Token List Parser}
Parsing rules determine the token list parser, and each parsing rule
is written in extended Scala parser combinators.  We modified the
meaning of the alternative composition operator ( \( ||| \) ) to collect
all the longest matched results.  If a parser detects a step that
cannot be parsed with given parsing rules, it reports the step into
{\sf Rule Assistant}.  Even when a parser parses a step successfully,
it also reports the step if it can parse the step in multiple ways.
We use Packrat parsing~\cite{packrat} for parsing rules, which
support left recursion.

@@

\subsection{Rule Assistant}
\begin{algorithm}[t]
  \caption{Fault Localization}\label{alg:fault}
  \begin{algorithmic}[1]
    \Function{FaultLocalize}{$T,n$}\Comment{$T$: failed step, $n$: size}
    \State $S = \varnothing$
    \For{$i = 0$ to $n - 1$}
    \For{$j = i$ to $n - 1$}
    \State $T'$ = a copy of $T$
    \State Substitute $T'[i..j]$ with $\tstar$
    \If{Parse($T'$) contains $\code{Dummy(}x \code{)}$ for some $x$}
    \State Insert $(x, i, j)$ into $S$
    \EndIf
    \EndFor
    \EndFor
    \While{$s = (x, i, j) \in S$}
    \If{$\exists (y, p, q) \in S$ s.t. $i \leq p \wedge q \leq j$}
    \State Remove $s$ from $S$
    \EndIf
    \EndWhile
    \State \Return $S$
    \EndFunction
  \end{algorithmic}
\end{algorithm}

To make it easy to write compile rules, we support a \textit{rule assistant},
which takes not-yet-convertible steps dubbed ``failed steps'' as arguments.
For each failed step, the rule assistant diagnoses a root cause of the
parsing failure.  The basic idea is to check whether we can parse the
failed input with the assumption that a specific sub-sequence of the
failed step is successfully parsed.  We define an approach to find
such sub-sequences of failed steps as \textit{fault localization}.
This approach was actually helpful for us when we update existing
compile rules for new versions of the specification.

The fault localization algorithm is shown in Algorithm~\ref{alg:fault}.
For a given failed step $T$ and the size of a failed input $n$, it
attempts to find a set of the most specific suggestions.  It
substitutes a specific sub-sequence \( T[i..j] \) of \( T \) with the
special token \( \tstar \), which represents some sub-sequence of a
failed step.  It collects a set of possible suggestions, and then
removes more general ones than existing suggestions.  To support this
process, we added a parsing rule  \( \code{starT} \) to each compile
rule as follows:
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = ... ||| starT ^^ { case x => Dummy("Stmt") }
// expressions
val Expr = ... ||| starT ^^ { case x => Dummy("Expr") }
\end{lstlisting}
where \( \code{starT} \) is a special basic token parser that just
checks whether a given token is the special token \( \tstar \). 
Its corresponding conversion rule is a function that returns a dummy
\( \ires \) component \( \code{Dummy} \) with a string value that
represents the name of its compile rule.

For example, let us assume that the \( \code{Expr} \) compile rule
does not have the alternative for lists:
\begin{lstlisting}[style=myScalastyle]
  "<<" ~ repsep(varT, ",") ~ ">>" ^^
       { case _ ~ x ~ _ => EList(e) } // lists
\end{lstlisting}
Then, the step 2-e-i of \textbf{ToPrimitive} becomes a failed step.
When we use the fault localization algorithm with the failed step and
its size 15, it first finds one suggestion for statements and four
suggestions for expressions as follows:
\[
\footnotesize
\! \! \! \!
  \begin{array}{c}
    (\scode{"Stmt"}, 0, 14), \;
    (\scode{"Expr"}, 3, 13), \;
    (\scode{"Expr"}, 4, 13), \;
    (\scode{"Expr"}, 6, 12), \;
    (\scode{"Expr"}, 10, 12)
  \end{array}
\]
In the \textbf{\small while} loop on lines 9--11, because the last one
is the most specific sub-sequence, it removes the other four
suggestions. Finally, the rule assistant suggests to define another
expression compile rule for the token list \hint{}.

>>>>

\subsection{Token List Parser}
Parsing rules determine the token list parser, and each parsing rule
is written in extended Scala parser combinators.  We modified the
meaning of the alternative composition operator ( \( ||| \) ) to collect
all the longest matched results.  If a parser detects a step that
cannot be parsed with given parsing rules, it reports the step into
{\sf Fault Localizer}.  Even when a parser parses a step successfully,
it also reports the step if it can parse the step in multiple ways.
We use Packrat parsing~\cite{packrat} for parsing rules, which
support left recursion.

@@

\subsection{Fault Localizer}\label{sec:localizer}
\begin{algorithm}[t]
  \caption{Fault Localization}\label{alg:fault}
  \begin{algorithmic}[1]
    \Function{FaultLocalize}{$T,n$}\Comment{$T$: failed step, $n$: size}
    \State $S = \varnothing$
    \For{$i = 0$ to $n - 1$}
    \For{$j = i$ to $n - 1$}
    \State $T'$ = a copy of $T$
    \State Substitute $T'[i..j]$ with $\tstar$
    \If{Parse($T'$) contains $\code{Dummy(}x \code{)}$ for some $x$}
    \State Insert $(x, i, j)$ into $S$
    \EndIf
    \EndFor
    \EndFor
    \While{$s = (x, i, j) \in S$}
    \If{$\exists (y, p, q) \in S$ s.t. $i \leq p \wedge q \leq j$}
    \State Remove $s$ from $S$
    \EndIf
    \EndWhile
    \State \Return $S$
    \EndFunction
  \end{algorithmic}
\end{algorithm}

To diagnose the root cause of parsing failures, we support a \textsf{Fault Localizer},
which takes not-yet-convertible steps dubbed ``failed steps'' as arguments.
The basic idea is to check whether we can parse the failed algorithm step
with the assumption that a specific sub-sequence of the
failed step is successfully parsed.  We define a \textit{rule suggestion}
as such sub-sequence of failed steps with the name of an existing compile rule.
\textsf{Fault Localizer} refines candidates of rule suggestions into
most specific ones. This approach was actually helpful for us when we update existing
compile rules for new versions of the specification.

The fault localization algorithm is shown in Algorithm~\ref{alg:fault}.
For a given failed step $T$ and the size of a failed input $n$, it
attempts to find a set of the most specific rule suggestions.  It
substitutes a specific sub-sequence \( T[i..j] \) of \( T \) with the
special token \( \tstar \), which represents some sub-sequence of a
failed step.  It collects a set of possible rule suggestions, and then
removes more general ones than existing suggestions.  To support this
process, we added a parsing rule  \( \code{starT} \) to each compile
rule as follows:
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = ... ||| starT ^^ { case x => Dummy("Stmt") }
// expressions
val Expr = ... ||| starT ^^ { case x => Dummy("Expr") }
\end{lstlisting}
where \( \code{starT} \) is a special basic token parser that just
checks whether a given token is the special token \( \tstar \). 
Its corresponding conversion rule is a function that returns a dummy
\( \ires \) component \( \code{Dummy} \) with a string value that
represents the name of its compile rule.

For example, let us assume that the \( \code{Expr} \) compile rule
does not have the alternative for lists:
\begin{lstlisting}[style=myScalastyle]
  "<<" ~ repsep(varT, ",") ~ ">>" ^^
       { case _ ~ x ~ _ => EList(e) } // lists
\end{lstlisting}
Then, the step 2-e-i of \textbf{ToPrimitive} becomes a failed step.
When we use the fault localization algorithm with the failed step and
its size 15, it first finds one rule suggestion for statements and four
rule suggestions for expressions as follows:
\[
\footnotesize
\! \! \! \!
  \begin{array}{c}
    (\scode{"Stmt"}, 0, 14), \;
    (\scode{"Expr"}, 3, 13), \;
    (\scode{"Expr"}, 4, 13), \;
    (\scode{"Expr"}, 6, 12), \;
    (\scode{"Expr"}, 10, 12)
  \end{array}
\]
In the \textbf{\small while} loop on lines 9--11, because the last one
is the most specific sub-sequence, it removes the other four
rule suggestions. Finally, \textsf{Fault Localizer} suggests to define
another expression compile rule for the token list \hint{}.

### 2019-08-24 icse20/conclusion.tex
assitant -> fault localizer

\section{Conclusion}\label{sec:conclude}
The annual updates of the ECMAScript specification makes it difficult to
build program analysis or formal verification of JavaScript due to the
required human efforts in modeling a moving target.  In this paper,
we proposed a tool \( \tool \), which \textit{automatically} extracts the
syntax and semantics specified in the ECMAScript specification.  The tool
generates a parser from a language grammar written in \( \bnfes \), and
compiles abstract algorithms written in English to \( \ires \) functions.
The only parts that require manual efforts are compile rules and
language-specific global setting, which we provide for ECMAScript
as an example case study.  We also support a rule assistant to guide
how to convert new abstract algorithms.  We evaluated \( \tool \) by
applying it to ECMAScript 2020 with Test262.  The extracted semantics
passed 19,220 of 19,282 applicable tests in Test262 and we showed
that the tool is also applicable to an incomplete language proposal.
The tool also detected six confirmed errors from the
specification and the proposal.  The implementation of the tool is
publicly available as an open-source project.

>>>>

\section{Conclusion}\label{sec:conclude}
The annual updates of the ECMAScript specification makes it difficult to
build program analysis or formal verification of JavaScript due to the
required human efforts in modeling a moving target.  In this paper,
we proposed a tool \( \tool \), which \textit{automatically} extracts the
syntax and semantics specified in the ECMAScript specification.  The tool
generates a parser from a language grammar written in \( \bnfes \), and
compiles abstract algorithms written in English to \( \ires \) functions.
The only parts that require manual efforts are compile rules and
language-specific global setting, which we provide for ECMAScript
as an example case study.  We also support \textsf{Fault Localizer} to
adapt updates of ECMAScript specification by suggesting new rules.
We evaluated \( \tool \) by applying it to ECMAScript 2020 with Test262.
The extracted semantics passed 19,220 of 19,282 applicable tests in Test262.
The tool also detected three confirmed errors from the specification.
Moreover, we showed that the tool is also applicable to an incomplete
language proposal. The implementation of the tool is publicly available
as an open-source project.

### 2019-08-24 icse20/eval.tex
Fixed typos
assitant -> fault localizer

\subsection{Correctness}
\begin{table}[t]
  \centering
  \caption{Testing results of Test262 for ECMAScript 2020}
  \label{table:test262}
\vspace*{-.5em}
\footnotesize
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All Test262 Tests} & \textbf{36,794}\\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes/Internationalisation & 1,774\\\hdashline
    In-progress features & 5,895\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{29,125}\\
    \aboverulesepcolor{gainsboro}\midrule
    Non-strict mode tests & 1,136\\\hdashline
    Module tests& 918 \\\hdashline
    Early error tests & 1,316\\\hdashline
    Inessential built-in object tests & 6,473\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{19,282}\\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & 19,220 \\\hdashline
    Failed tests & 62 \\\bottomrule
  \end{tabular}
\vspace*{-1em}
\end{table}

To evaluate the correctness of \( \tool \), we developed a JavaScript
interpreter based on the extracted syntax and semantics from
ECMAScript 2020.  Among 9,657 steps in ECMAScript 2020,
8,926 steps are automatically compiled via \textsf{Algorithm Compiler}.
Among the remaining 731 steps, we selected 381 steps
that are essential to the core semantics and manually
implemented their corresponding \( \ires \) functions
via the rule assistant introduced in Section~\ref{sec:assistant}.
Moreover, we implement the \textsf{Global Setting} except
the excluded language features discussed in Section~\ref{sec:exclusion}.

>>>>

\subsection{Correctness}
\begin{table}[t]
  \centering
  \caption{Testing results of Test262 for ECMAScript 2020}
  \label{table:test262}
\vspace*{-.5em}
\footnotesize
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All Test262 Tests} & \textbf{36,794}\\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes/Internationalization & 1,774\\\hdashline
    In-progress features & 5,895\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{29,125}\\
    \aboverulesepcolor{gainsboro}\midrule
    Non-strict mode tests & 1,136\\\hdashline
    Module tests& 918 \\\hdashline
    Early error tests & 1,316\\\hdashline
    Inessential built-in object tests & 6,473\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{19,282}\\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & 19,220 \\\hdashline
    Failed tests & 62 \\\bottomrule
  \end{tabular}
\vspace*{-1em}
\end{table}

To evaluate the correctness of \( \tool \), we developed a JavaScript
interpreter based on the extracted syntax and semantics from
ECMAScript 2020.  Among 9,657 steps in ECMAScript 2020,
8,926 steps are automatically compiled via \textsf{Algorithm Compiler}.
Among the remaining 731 steps, we selected 381 steps
that are essential to the core semantics and manually
implemented their corresponding \( \ires \) functions
via the \textsf{Fault Localizer} introduced in Section~\ref{sec:localizer}.
Moreover, we implement the \textsf{Global Setting} except
the excluded language features discussed in Section~\ref{sec:exclusion}.

### 2019-08-24 icse20/related.tex
assitant -> fault localizer

In the field of automatic model generation, the closest related work to
ours is \citet{javadoc}'s, which generates Java code from Javadoc comments
for API functions.  Using NLP techniques and various heuristic methods,
it produces several candidate code tests them with actual implementation
of the API functions to find correct modeling.  Unlike their approach, we
support a specification translation assistant to support future language
updates and to provide correct meaning of specification, which is
applicable for testing even when the actual implementation is not available.

@@

Several approaches have defined the formal semantics of JavaScript.
\citet{lambdajs} defined a core calculus of JavaScript, and expressed the
rest as desugaring.  While it presents the core JavaScript semantics in
an extension of the $\lambda$ calculus, it does not show the semantics
correspondence defined in the ECMAScript specification.  KJS~\citet{kjs} and
JaVerT~\citet{javert} defined formal semantics of JavaScript by manually converting
the ECMAScript specification to their own formal languages.  KJS mapped
ECMAScript 5.1 in the K framework~\cite{kframework}, which can be used
for program verification and analysis.  Similarly, JaVerT converts the
specification to their own IR called JSIL to make further analysis.
Our approach provides a framework to generate syntactic parsers and
semantics compilers from the specification to \( \ires \)
with a conversion assistant, which reduces human efforts significantly.

>>>>

In the field of automatic model generation, the closest related work to
ours is \citet{javadoc}'s, which generates Java code from Javadoc comments
for API functions.  Using NLP techniques and various heuristic methods,
it produces several candidate code tests them with actual implementation
of the API functions to find correct modeling.  Unlike their approach, we
introduce a fault localization algorithm to support future language
updates and to provide correct meaning of specification. Our tool is also
applicable for testing even when the actual implementation is not available.

@@

Several approaches have defined the formal semantics of JavaScript.
\citet{lambdajs} defined a core calculus of JavaScript, and expressed the
rest as desugaring.  While it presents the core JavaScript semantics in
an extension of the $\lambda$ calculus, it does not show the semantics
correspondence defined in the ECMAScript specification.  KJS~\citet{kjs} and
JaVerT~\citet{javert} defined formal semantics of JavaScript by manually converting
the ECMAScript specification to their own formal languages.  KJS mapped
ECMAScript 5.1 in the K framework~\cite{kframework}, which can be used
for program verification and analysis.  Similarly, JaVerT converts the
specification to their own IR called JSIL to make further analysis.
Our approach provides a mechanized framework to synthesize syntactic parsers and
to automatically extract semantics from the specification to \( \ires \)
using rule-based compilation technique. It significantly reduces human
efforts and also flexible for future specification updates.
